\dppTitle

### 2014-03-06 manuscripts/dpp-msbayes/dpp-msbayes-abstract.tex
Updating abstract for dpp ms.
Adding section titles to the abstract per bmc guidelines. The
bmc-specific section title commands are wrapped in `ifbmc` statements.

To understand the processes that generate biodiversity, it is
important to account for large-scale processes that affect the evolutionary
history of groups of co-distributed populations of organisms.
Such events predict temporally clustered divergences times, a pattern
that can be estimated using genetic data from co-distributed species.
I introduce a new approximate-Bayesian method for comparative
phylogeographical model-choice that estimates the temporal distribution of
divergences across taxa from multi-locus DNA sequence data.
The model is an extension of that implemented in \msb.
By reparameterizing the model, introducing more flexible priors on
demographic and divergence-time parameters, and implementing a
non-parametric Dirichlet-process prior over divergence models, I improved
the robustness, accuracy, and power of the method for estimating shared
evolutionary history across taxa.
The results demonstrate the improved performance of the new method is due
to (1) more appropriate priors on divergence-time and demographic
parameters that avoid prohibitively small marginal likelihoods for models
with more divergence events,
and (2) the Dirichlet-process providing a flexible prior on divergence
histories that does not strongly disfavor models with intermediate numbers
of divergence events.
% The results demonstrate that the tendency of the \msb model to spuriously
% support models of clustered divergences is caused by a combination of (1)
% uniform priors on nuisance parameters hindering the marginal likelihoods of
% models with more divergence-time parameters, and (2) a prior on divergence
% models that disfavors models with intermediate numbers of divergence-time
% parameters.
The new method yields more robust estimates of posterior uncertainty, and
thus greatly reduces the tendency of the model to incorrectly estimate
biogeographically interesting models with strong support.

>>>>

\ifbmc{\parttitle{Background}}{}
To understand the processes that generate biodiversity, it is
important to account for large-scale processes that affect the evolutionary
history of groups of co-distributed populations of organisms.
Such events predict temporally clustered divergences times, a pattern
that can be estimated using genetic data from co-distributed species.
I introduce a new approximate-Bayesian method for comparative
phylogeographical model-choice that estimates the temporal distribution of
divergences across taxa from multi-locus DNA sequence data.
The model is an extension of that implemented in \msb.
\ifbmc{\parttitle{Results}}{}
By reparameterizing the model, introducing more flexible priors on
demographic and divergence-time parameters, and implementing a
non-parametric Dirichlet-process prior over divergence models, I improved
the robustness, accuracy, and power of the method for estimating shared
evolutionary history across taxa.
\ifbmc{\parttitle{Conclusions}}{}
The results demonstrate the improved performance of the new method is due
to (1) more appropriate priors on divergence-time and demographic
parameters that avoid prohibitively small marginal likelihoods for models
with more divergence events,
and (2) the Dirichlet-process providing a flexible prior on divergence
histories that does not strongly disfavor models with intermediate numbers
of divergence events.
% The results demonstrate that the tendency of the \msb model to spuriously
% support models of clustered divergences is caused by a combination of (1)
% uniform priors on nuisance parameters hindering the marginal likelihoods of
% models with more divergence-time parameters, and (2) a prior on divergence
% models that disfavors models with intermediate numbers of divergence-time
% parameters.
The new method yields more robust estimates of posterior uncertainty, and
thus greatly reduces the tendency of the model to incorrectly estimate
biogeographically interesting models with strong support.
